Designing a Search for the BBC

### 2014-02-05 paper.tex
Renamed coursework file to paper.

\usepackage{graphicx}
\usepackage{rotating}
\usepackage{verbatim}
\usepackage{url}

@@

Using \emph{Soft Systems Methodology} (SSM)
\cite{checkland2006learning}, we can stand back from
an ontological approach of defining what the search system \emph{is} or
\emph{comprises} and instead take an \emph{epistemological} view of search
as a system. With this view, we could consider a system that holistically
transforms members of the public's desires to find online content into
the consumption of that content -- whether those desires are \emph{precise}
(e.g. they want an exact article known by headline they saw earlier or a
particular programme they missed on television) or those desires are
\emph{fuzzy} (e.g. news about a certain topic, any comedy programme, learning
materials about the Industrial Revolution).

Checkland and Scoles \cite{checkland1990soft} decribed a \emph{Rich Picture} approach
for representing a problem situation early in SSM approaches.
Given the size and complexity of the
search system as a whole, a useful initial step is to create such an informal
representation of what is known about the problem. Figure~\ref{rich-picture}
shows what I know of the audience, search and most BBC online content areas.
Note that not all areas are covered and a strong emphasis is placed on TV
catch-up (e.g. via the iPlayer product). Radio catch-up is not mentioned
as it shares a lot of similarity with television in terms of use and any
differences are out of scope for this design.

@@

This is not to say that we can simply cross off certain elements from
our depiction of the problem because they do not directly interact
with the subsystem being designed. The \emph{systems thinking} approach
advocated by Checkland \cite{checkland1999systems} encourages us to
consider the irreducible properties of each system at each level
of abstraction. Thus we need to consider not only a search application
subsystem that solves specific problems for its immediate users, but
also an application that contributes to the desirable, emergent
properties of the BBC service as a whole.

@@

The key design decision in figure~\ref{sequence-producer} is the use of
asynchronous messages only. A non-blocking set of interactions such as
publish-subscribe \cite{hohpe2004enterprise} is a good way to decouple
systems that produce and store progamme information from the search
application systems. If the systems surrounding the programmes database
can be built a \emph{channel adapter} \cite{hohpe2004enterprise} to integrate
it to a messaging system, then the search indexes can receive changes to
information without TV producers, journalists, content
editors, etc. even being aware this is happening.

Note in figure~\ref{sequence-user} that while the search indexes
will contain representations of content
from several source systems, the intention shown is that richer information
about the domain model will not be held in the search indexes. This goes
along with the principle of separation of concerns \cite{dijkstra1982role}
in that the search index component can focus on optimising its data
structures around retrieval. This kind of modularity also allows source
systems maintained by other teams to take the responsibility of the
accuracy of the information, which fits in with the wider holistic view
of the system: the volume of information involved requires that
separate teams are responsible for the accuracy of their data.

This can be seen as similar to the \emph{Lazy Load} pattern
\cite{fowler2002patterns} in that the search indexes will only return
stub objects that are capable of retrieving the fuller information
to need. This, however, could lead to a lot of calls to different
service applications per page of results. This can be done in parallel, but
the fact still remains that the user has to wait for all this to
assemble before seeing even one result.

One solution to this in modern web application design is to
push the lazy loading into the web browser using AJAX. \cite{garrett2005ajax}
Such a solution is depicted in figure~\ref{sequence-ajax}. Whilst
this still requires just as many calls to backend services --
perhaps even more complexity as the calls are going through
more layers -- it can give a user experience that appears more responsive.

@@

It has been expressed already that a BBC-wide search application
is going to have to index, retrieve and display a diverse set of
information. Parts of the application might well want to incorporate
a domain model \cite{fowler2002patterns} so as to understand how
to perform each of these actions against each possible item
the search application could return as a search result. A maximal
model is shown in figure~\ref{model} that attempts to capture
a good proportion of the content and concepts the BBC has
been attempting to model over several years. This model is
an aggregate of individual ontologies developed for specific purposes,
but given the search application has to provide the discovery for
the full set of this information, it is not unreasonable that
a search application would have a domain model that covers the totality.

Note that complexity of information for programmes alone. \cite{raimond2009bbc}
A programme to a member of the public could actually refer to an
exact episode or indeed the \emph{brand}, i.e. the title of the programme
in general. An example of a brand would be
\emph{Doctor Who}, which itself contains multiple series, which in turn
contain a collection of episodes. Note that the brand itself has episodes
as immediate children that do not live under a series, e.g. Christmas specials.
It is also the case that certain things do not have brands or series, e.g.
a film is modelled as a one-off episode.

@@

The model also skims the surface of the sport ontology \cite{rayfield2011bbc}
created before the 2012 Olympic games, which aims to model the whole domain
of sporting personalities, events and competitions (and more). This might
be too fine-grained for the domain model used within the search application,
but it is likely that people will want to search for competitions like
``World Cup'' or sporting disciplines such as ``football''. A search application
that understands these concepts as entities in their own right may well
be able to direct users at a curated, dedicated ``home page'' thereof alongside
simply matching articles and other works that contain those terms.

@@

The sequence diagram for the producer (or any other content creator)
indirectly getting their content into the search system demonsrates
the need for asynchronous messaging (and publish-subscribe), but
the nuances of such a process are not comprehensively shown in
this format. A better illutration for such a message-based integration
system might be derived from the illutrated patterns created
by Hohpe and Woolf. \cite{hohpe2004enterprise}

The behaviour of the query web application in figure~\ref{sequence-user}
is defined with a hard line
taken on keeping the information stored in the indexes to a minimum.
At a basic level, this is not unlike a \emph{content enricher} pattern
\cite{hohpe2004enterprise} whereby the search application
business layer enriches the stubs in the indexes with information
the source system (the index) simply does not have. At a more purist
extreme, this could follow a \emph{claim check} pattern where
the index returns only globally-unique identifiers for the matching
items and makes no attempt to present any other knowledge about them
(and thus avoids any synchronisation issues if an item is updated at
source).

@@

These decisions relate to how the system would implement the data model
in figure~\ref{model}. The onotology described is an aggregation
of several efforts by Raimond \cite{raimond2009bbc}, Rayfield
\cite{rayfield2011bbc} and others -- along with some additional work
to join them together -- to represent the wealth of
information with which the BBC deals. It could be argued both that
a search application that \emph{understands} this diversity of
content must reflect it in its domain model but that a search
application that is \emph{coupled} to the individual ontologies
in this way is brittle with regard to changes therein. Duplication
would only harm maintainability.

Thus the domain model given in figure~\ref{model} should only serve
as a communication artefact that leads to further development of
a domain model more suitable to the needs of the search application
without the burden of maintaining more than is necessary. The use
of \emph{subtype polymorphism} \cite{booch2007object} is likely
to be key to ensure the search domain model contains only the APIs
it needs. For example, does the search application have a need
to differentiate between a \emph{NewsItem} and a \emph{BlogPost}
for the purposes of displaying the search result's title? If the
CreativeWork top-level class has a title property, then the domain
model so far to enable that one behaviour needs only one class!

The application could go further and interact via a single
SearchResult \emph{facade} \cite{fowler2002patterns} whose
instances provide appropriate responses to canonical hooks
such as \emph{getDisplayTitle()} and \emph{getDestinationUrl()}
via polymorphic \emph{composition} with different target classes
from the fuller domain model. Given that the search indexes
are likely to take in content from any number of future systems,
there is an appeal to taking a schemaless approach \cite{sadalage2012nosql}
and allow the search application's view layer to display
different kinds of results differently via \emph{duck typing}.
\cite{python2013ducktyping}

A dynamic, schema-free domain model used within the search application
-- noting that, of course, schemaless truly means there is an
implicit schema in the logic that creates these dynamic objects from
source systems \cite{sadalage2012nosql} -- could prove to aid the
search system's need to model different kinds of data in the same
index. For example, our designers might express a desire to put
small summaries of weather forecasts within search results that
contain places. In the static sense, we could say that anything
of \emph{Place} type is displayed with such a feature. With
a dynamic, duck-typed model, we could ask
``does this item have weather?'' in place of ``is this a place?'', thus
allowing for the future design that extends forecasts to football
matches (since football matches are \emph{Event}s that occur in
a \emph{Place}, it is reasonable for a weather property to be
set thereon).

Overall, we have some promising, high-level models from which to
start making such more fine-grained decisions about the search
application. The use cases are likely sufficient for early iterations
or a \emph{Minimal Viable Product} \cite{junk2000dynamic} and
the behaviours capture the overall needs of the system. There is still
much scope for returning to our systems thinking and Soft Systems
Methodology to monitor the general model for Checkland's ``3 Es''
(efficacy, efficiency and effectiveness) \cite{checkland1990soft},
which is only briefly touched on in my attempts to relate the
data model to the user's interaction with the system.

@@

Even the models that are presented in this report do not paint the full
picture, but it could be argued that it is not their purpose to do so.
As stated at the end of section~\ref{appraisal}, the use case diagram
provides a starting point that might be sufficient for an early
iteration of a project in an \emph{Agile} methodology. \cite{beck2001agile}

@@

Some of this hints at a drawback of UML modelling being that it encourages
a lot of design decision at an early stage of a project -- a stage at which we arguably
have the least information. \cite{kelly2013conway} However, there are plenty of
efforts in spite of this that promote modelling and UML being used
compatibly within an Agile process. The use of other modelling techniques
in an Agile setting such as
Rational Unified Process (RUP) and Agile Unified Process (AUP) have been
suggested as suitable in an Agile project.
\cite{ambler2002agile} It may have been more suitable to incorporate
a more diverse range of modelling techniques in the design and analysis
presented so as to find the true strengths of each respective approach.

>>>>

\usepackage{graphicx}
\usepackage{rotating}
\usepackage{verbatim}
\usepackage{url}
\usepackage[square]{natbib}

@@

Using \emph{Soft Systems Methodology} (SSM)
\citep{checkland2006learning}, we can stand back from
an ontological approach of defining what the search system \emph{is} or
\emph{comprises} and instead take an \emph{epistemological} view of search
as a system. With this view, we could consider a system that holistically
transforms members of the public's desires to find online content into
the consumption of that content -- whether those desires are \emph{precise}
(e.g. they want an exact article known by headline they saw earlier or a
particular programme they missed on television) or those desires are
\emph{fuzzy} (e.g. news about a certain topic, any comedy programme, learning
materials about the Industrial Revolution).

Checkland and Scoles \citep{checkland1990soft} decribed a \emph{Rich Picture} approach
for representing a problem situation early in SSM approaches.
Given the size and complexity of the
search system as a whole, a useful initial step is to create such an informal
representation of what is known about the problem. Figure~\ref{rich-picture}
shows what I know of the audience, search and most BBC online content areas.
Note that not all areas are covered and a strong emphasis is placed on TV
catch-up (e.g. via the iPlayer product). Radio catch-up is not mentioned
as it shares a lot of similarity with television in terms of use and any
differences are out of scope for this design.

@@

This is not to say that we can simply cross off certain elements from
our depiction of the problem because they do not directly interact
with the subsystem being designed. The \emph{systems thinking} approach
advocated by Checkland \citep{checkland1999systems} encourages us to
consider the irreducible properties of each system at each level
of abstraction. Thus we need to consider not only a search application
subsystem that solves specific problems for its immediate users, but
also an application that contributes to the desirable, emergent
properties of the BBC service as a whole.

@@

The key design decision in figure~\ref{sequence-producer} is the use of
asynchronous messages only. A non-blocking set of interactions such as
publish-subscribe \citep{hohpe2004enterprise} is a good way to decouple
systems that produce and store progamme information from the search
application systems. If the systems surrounding the programmes database
can be built a \emph{channel adapter} \citep{hohpe2004enterprise} to integrate
it to a messaging system, then the search indexes can receive changes to
information without TV producers, journalists, content
editors, etc. even being aware this is happening.

Note in figure~\ref{sequence-user} that while the search indexes
will contain representations of content
from several source systems, the intention shown is that richer information
about the domain model will not be held in the search indexes. This goes
along with the principle of separation of concerns \citep{dijkstra1982role}
in that the search index component can focus on optimising its data
structures around retrieval. This kind of modularity also allows source
systems maintained by other teams to take the responsibility of the
accuracy of the information, which fits in with the wider holistic view
of the system: the volume of information involved requires that
separate teams are responsible for the accuracy of their data.

This can be seen as similar to the \emph{Lazy Load} pattern
\citep{fowler2002patterns} in that the search indexes will only return
stub objects that are capable of retrieving the fuller information
to need. This, however, could lead to a lot of calls to different
service applications per page of results. This can be done in parallel, but
the fact still remains that the user has to wait for all this to
assemble before seeing even one result.

One solution to this in modern web application design is to
push the lazy loading into the web browser using AJAX. \citep{garrett2005ajax}
Such a solution is depicted in figure~\ref{sequence-ajax}. Whilst
this still requires just as many calls to backend services --
perhaps even more complexity as the calls are going through
more layers -- it can give a user experience that appears more responsive.

@@

It has been expressed already that a BBC-wide search application
is going to have to index, retrieve and display a diverse set of
information. Parts of the application might well want to incorporate
a domain model \citep{fowler2002patterns} so as to understand how
to perform each of these actions against each possible item
the search application could return as a search result. A maximal
model is shown in figure~\ref{model} that attempts to capture
a good proportion of the content and concepts the BBC has
been attempting to model over several years. This model is
an aggregate of individual ontologies developed for specific purposes,
but given the search application has to provide the discovery for
the full set of this information, it is not unreasonable that
a search application would have a domain model that covers the totality.

Note that complexity of information for programmes alone. \citep{raimond2009bbc}
A programme to a member of the public could actually refer to an
exact episode or indeed the \emph{brand}, i.e. the title of the programme
in general. An example of a brand would be
\emph{Doctor Who}, which itself contains multiple series, which in turn
contain a collection of episodes. Note that the brand itself has episodes
as immediate children that do not live under a series, e.g. Christmas specials.
It is also the case that certain things do not have brands or series, e.g.
a film is modelled as a one-off episode.

@@

The model also skims the surface of the sport ontology \citep{rayfield2011bbc}
created before the 2012 Olympic games, which aims to model the whole domain
of sporting personalities, events and competitions (and more). This might
be too fine-grained for the domain model used within the search application,
but it is likely that people will want to search for competitions like
``World Cup'' or sporting disciplines such as ``football''. A search application
that understands these concepts as entities in their own right may well
be able to direct users at a curated, dedicated ``home page'' thereof alongside
simply matching articles and other works that contain those terms.

@@

The sequence diagram for the producer (or any other content creator)
indirectly getting their content into the search system demonsrates
the need for asynchronous messaging (and publish-subscribe), but
the nuances of such a process are not comprehensively shown in
this format. A better illutration for such a message-based integration
system might be derived from the illutrated patterns created
by Hohpe and Woolf. \citep{hohpe2004enterprise}

The behaviour of the query web application in figure~\ref{sequence-user}
is defined with a hard line
taken on keeping the information stored in the indexes to a minimum.
At a basic level, this is not unlike a \emph{content enricher} pattern
\citep{hohpe2004enterprise} whereby the search application
business layer enriches the stubs in the indexes with information
the source system (the index) simply does not have. At a more purist
extreme, this could follow a \emph{claim check} pattern where
the index returns only globally-unique identifiers for the matching
items and makes no attempt to present any other knowledge about them
(and thus avoids any synchronisation issues if an item is updated at
source).

@@

These decisions relate to how the system would implement the data model
in figure~\ref{model}. The onotology described is an aggregation
of several efforts by Raimond \citep{raimond2009bbc}, Rayfield
\citep{rayfield2011bbc} and others -- along with some additional work
to join them together -- to represent the wealth of
information with which the BBC deals. It could be argued both that
a search application that \emph{understands} this diversity of
content must reflect it in its domain model but that a search
application that is \emph{coupled} to the individual ontologies
in this way is brittle with regard to changes therein. Duplication
would only harm maintainability.

Thus the domain model given in figure~\ref{model} should only serve
as a communication artefact that leads to further development of
a domain model more suitable to the needs of the search application
without the burden of maintaining more than is necessary. The use
of \emph{subtype polymorphism} \citep{booch2007object} is likely
to be key to ensure the search domain model contains only the APIs
it needs. For example, does the search application have a need
to differentiate between a \emph{NewsItem} and a \emph{BlogPost}
for the purposes of displaying the search result's title? If the
CreativeWork top-level class has a title property, then the domain
model so far to enable that one behaviour needs only one class!

The application could go further and interact via a single
SearchResult \emph{facade} \citep{fowler2002patterns} whose
instances provide appropriate responses to canonical hooks
such as \emph{getDisplayTitle()} and \emph{getDestinationUrl()}
via polymorphic \emph{composition} with different target classes
from the fuller domain model. Given that the search indexes
are likely to take in content from any number of future systems,
there is an appeal to taking a schemaless approach \citep{sadalage2012nosql}
and allow the search application's view layer to display
different kinds of results differently via \emph{duck typing}.
\citep{python2013ducktyping}

A dynamic, schema-free domain model used within the search application
-- noting that, of course, schemaless truly means there is an
implicit schema in the logic that creates these dynamic objects from
source systems \citep{sadalage2012nosql} -- could prove to aid the
search system's need to model different kinds of data in the same
index. For example, our designers might express a desire to put
small summaries of weather forecasts within search results that
contain places. In the static sense, we could say that anything
of \emph{Place} type is displayed with such a feature. With
a dynamic, duck-typed model, we could ask
``does this item have weather?'' in place of ``is this a place?'', thus
allowing for the future design that extends forecasts to football
matches (since football matches are \emph{Event}s that occur in
a \emph{Place}, it is reasonable for a weather property to be
set thereon).

Overall, we have some promising, high-level models from which to
start making such more fine-grained decisions about the search
application. The use cases are likely sufficient for early iterations
or a \emph{Minimal Viable Product} \citep{junk2000dynamic} and
the behaviours capture the overall needs of the system. There is still
much scope for returning to our systems thinking and Soft Systems
Methodology to monitor the general model for Checkland's ``3 Es''
(efficacy, efficiency and effectiveness) \citep{checkland1990soft},
which is only briefly touched on in my attempts to relate the
data model to the user's interaction with the system.

@@

Even the models that are presented in this report do not paint the full
picture, but it could be argued that it is not their purpose to do so.
As stated at the end of section~\ref{appraisal}, the use case diagram
provides a starting point that might be sufficient for an early
iteration of a project in an \emph{Agile} methodology. \citep{beck2001agile}

@@

Some of this hints at a drawback of UML modelling being that it encourages
a lot of design decision at an early stage of a project -- a stage at which we arguably
have the least information. \citep{kelly2013conway} However, there are plenty of
efforts in spite of this that promote modelling and UML being used
compatibly within an Agile process. The use of other modelling techniques
in an Agile setting such as
Rational Unified Process (RUP) and Agile Unified Process (AUP) have been
suggested as suitable in an Agile project.
\citep{ambler2002agile} It may have been more suitable to incorporate
a more diverse range of modelling techniques in the design and analysis
presented so as to find the true strengths of each respective approach.
